SDR enhancement by clouds

### 2024-03-24 article/article.Rmd
Commit 2024-03-24 18:14

We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
as reference. 
by an empirica approach by inspecting a set of chosen days.

we adjusted teh threshold for each and chek then results

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs,
thus we used a relative factor, to create an upper envelope of the clear sky
irradiance, above which, any GHI value can safely attributed to CE.

To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
manual inspection of the CE identification, on specially selected days from the whole
dataset.  We used seven sets of selected days, with characteristics relevant to the
efficiency of the identification threshold.  These sets were random groups of about
20 to 30 days with the following characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) without clouds and without EC events,
(e) with at least $60\%$ of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

<!-- - some manual selected days that were included during the manual inspection -->
<!-- - 20 days with the largest over irradiance CE events -->
<!-- - 30 days with largest total over irradiance -->
<!-- - 20 days without clouds (CSid) @Natsis2023 -->
<!-- - any day without clouds and EC events -->
<!-- - 20 days with at least 60% of day length without clouds and some EC events -->
<!-- - 30 random days -->
<!-- - some manual selected days that were included during the manual inspection -->

>>>>

The use of the actual modeled values of clear sky GHI alone, can not provide us with
a robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs, thus
we used a relative factor, to create an upper envelope of the clear sky irradiance,
above which, any GHI value can safely attributed to CE.  We evaluated the performance
of the modeled clear radiation for each of atmospheric level of clearness, as
reference, in order to conclude which is the most appropriate.

To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
implemented an empirical method, by manual inspection of the CE identification, on
specially selected days from the whole dataset.  We used seven sets of selected days,
with characteristics relevant to the efficiency of the identification threshold.
These sets were random groups of about 20 to 30 days with the following
characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) without clouds and without EC events,
(e) with at least $60\%$ of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

@@

### 2024-03-24 article/article.tex
Commit 2024-03-24 18:14

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-23}

@@

We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
as reference.
by an empirica approach by inspecting a set of chosen days.

we adjusted teh threshold for each and chek then results

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs,
thus we used a relative factor, to create an upper envelope of the clear sky
irradiance, above which, any GHI value can safely attributed to CE.

To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
manual inspection of the CE identification, on specially selected days from the whole
dataset. We used seven sets of selected days, with characteristics relevant to the
efficiency of the identification threshold. These sets were random groups of about
20 to 30 days with the following characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
(d) without clouds and without EC events,
(e) with at least \(60\%\) of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-24}

@@

The use of the actual modeled values of clear sky GHI alone, can not provide us with
a robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs, thus
we used a relative factor, to create an upper envelope of the clear sky irradiance,
above which, any GHI value can safely attributed to CE. We evaluated the performance
of the modeled clear radiation for each of atmospheric level of clearness, as
reference, in order to conclude which is the most appropriate.

To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
implemented an empirical method, by manual inspection of the CE identification, on
specially selected days from the whole dataset. We used seven sets of selected days,
with characteristics relevant to the efficiency of the identification threshold.
These sets were random groups of about 20 to 30 days with the following
characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
(d) without clouds and without EC events,
(e) with at least \(60\%\) of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

@@
